---
title: "Final Project Precis"
author: "Michael Calabro"
date: "10/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(Lahman)
library(readr)

B_2017 <- read_csv("Batting_2017.csv")
```

## My Project Idea

My plan is to use Sean Lahman's Baseball database to investigate and expound upon a curious baseball statistic that I saw online earlier this semester. Namely, I wish to investigate potential causes of the fact that total strikeouts in the MLB have increased year over year for the past thirteen years. As of now, I have access to the Lahman dataset, which I could access as a package in R, but it only goes up to 2016. However, on Sean Lahman's website, there is data up to 2017, so I added this to my repo, and below I have the summary of the strikeout statistic. 

```{r}
B_2017 %>%
  filter(yearID %in% 2000:2017) %>%
  group_by(yearID) %>%
  summarise(total_SO = sum(SO)) %>%
  arrange(desc(yearID))
```

My plan is to create a shiny app which one can use to view different relations between different batting and pitching statistics which may be relevant to the curious strikeout stat.
